\begin{longtable}{|p{0.5cm}|p{2.5cm}|p{4cm}|p{6cm}|}
\caption{Data environment representation requirements for GOND-NRDS use case.\label{tab1}}\\

\hline
\textbf{S\#} &  \textbf{Requirement}  &  \textbf{Description}  &  \textbf{Example in use case} \\
\hline
\endfirsthead

\hline
\textbf{S\#} &  \textbf{Requirement}  &  \textbf{Description}  &  \textbf{Example in use case} \\
\hline
\endhead
01 &  Data controller and processor  &  To represent data controller and processors with their types (i.e. authority, organisation, or individual), tasks and responsibilities within given time and environment &  As GOND  and NRDS is a type of organisation data controller and processor. GOND is data controller with direct responsibility of his environment and indirect responsibility for NRDS environment. GOND is also a data processor, it generate datasets for NRDS and open environment\\
\hline
02 &  Data subjects and users  &  This represent the information of data subjects (i.e. id, name, age, related consent). And the intended users of data  & In GOND-NRDS use case independent researchers and public in open environment are types of data users.   \\
\hline
03 &  Essential means of data collection and type of data  &  This describe the purpose of data collection and type of data. is collected data is personal  &  GONDs collect data from its partners for effective decision making and sharing of data with public because of legal obligations   \\
\hline
04 &  Data and data variables &  A kind of collected, processed, and shared data  &  GOND generate a set of data for NRDS and open environment \\
\hline
05 &  Processes  &  A kind of activity that changes the state of data  or any mechanism that is used for auditing purpose &  A data service at GOND that pass on data by checking some agreement protocols \\
\hline
06 &  Access and control (Direct and Indirect)  &  How to show the access and control mechanism over the data and services &  GOND has service that can be access by the NRDS  based on some contract signed by them. GOND has also indirect control over the data release from the NRDS environment  \\
\hline
07 &  Contract/ Protocols &  These are contracts among the data controller, processor and might be users to access, use and sharing of data  &  GOND has service that is used by the NRDS  based on some contract signed by them. GOND has also indirect control over the data release from the NRDS environment  \\
\hline
08 &  Relations &  This describes the possible  relationship from environment to environment or its internal elements    &  By using the knowledge from the relationship the information about data subjects can be identified. On the other hand the relations among the data controller, and data users can reduce the risk to the data in the intended environment. \\

\hline
09 &  Environments &  That shows the contextual boundaries for data controller, data processor,  data users,  data sharing, data situation, etc. Environment also defines the locus of control and locus of responsibility.  & GOND and NRDS are two closed environments . Wheres data output from the independent researchers in the publications is an open environment \\
\hline
10 &  Environments in environments &  Sometimes an environment may contain other environments along with users, data, and process. And data flows in the same organisation's sub units for processing, auditing, etc. & NRDS-environment and research lab for independent researchers environment are in  Barestshire university-environment is an example of Environments in environments \\
\hline
11 &  Identifiers &  A unique identifier for data controller, data processors, a piece of data content, environment, etc & How to uniquely identify process, data, users, controller in GOND and NRDS's environment   \\
\hline
12 & Duration and Age & How long the data is collected, processed, and controlled by the various environments during the life cycle. Age of data when it is ready for use  & How long the GOND takes time to pass on data to the NRDS. Might be the one week old data is not more useful for the independent researchers.   \\
\hline
\end{longtable}


\begin{longtable}
\caption{Data Environment representation requirements for GOND-NRDS use case }\label{tab1}
\begin{tabularx}{\linewidth}{ 
  | >{\raggedright\arraybackslash}X 
  | >{\raggedright\arraybackslash}X 
    | >{\raggedright\arraybackslash}X 
  | >{\raggedright\arraybackslash}X | }
\hline
\textbf{S\#} &  \textbf{Representation Requirement}  &  \textbf{Description}  &  \textbf{Example in GOND-NRDS use case} \\
\hline
01 &  Data controller and processor  &  To represent data controller and processors with their types (i.e. authority, organisation, or individual), tasks and responsibilities within given time and environment &  As GOND  and NRDS is a type of organisation data controller and processor. GOND is data controller with direct responsibility of his environment and indirect responsibility for NRDS environment. GOND is also a data processor, it generate datasets for NRDS and open environment\\
\hline
01 &  Data subjects and users  &  This shows the information of data subjects (i.e. id, name, age, related consent). And the intended users of data  &  There are two types of users in GOND-NRDS use case. The first one are independent researchers and the second are public that uses data from the open environment. The data subjects are not discussed in this use case  \\
\hline
02 &  Essential means of data collection and type of data  &  This describe the purpose of data collection and type of data. is collected data is personal  &  GONDs collect data from its partners for effective decision making and sharing of data with public because of legal obligations   \\
\hline
03 &  Variables in collected data and shared data &  A kind of collected, processed, and shared data  &  GOND generate a set of data for NRDS and open environment \\
\hline
04 &  Processes  &  A kind of activity that changes the state of data  or any mechanism that is used for auditing purpose &  A data service at GOND that pass on data by checking some agreement protocols \\
\hline
05 &  Access and control (Direct and Indirect)  &  How to show the access and control mechanism over the data and services &  GOND has service that can be access by the NRDS  based on some contract signed by them. GOND has also indirect control over the data release from the NRDS environment  \\
\hline
06 &  Agreement/Contract/Protocols &  These are contracts among the data controller, processor and might be users to access, use and sharing of data  &  GOND has service that is used by the NRDS  based on some contract signed by them. GOND has also indirect control over the data release from the NRDS environment  \\
\hline
07 &  Relations &  This describes the possible  relationship among the data collectors, data subjects, data collectors, data processors, data users    &  By using the knowledge from the relationship the information about data subjects can be identified. On the other hand the relations among the data controller, data processors and data users can reduce the risk to the data in the intended environment. \\

\hline
08 &  Environments &  That shows the contextual boundaries for data controller, data processor,  data users,  data sharing, data situation, etc. Environment also defines the locus of control and locus of responsibility.  & GOND and NRDS are two closed environments . Wheres data output from the independent researchers in the publications is an open environment \\
\hline
09 &  Environments in environments &  Sometimes an environment may contain other environments along with users, data, and process. And data flows in the same organisation's sub units for processing, auditing, etc. & NRDS-environment and research lab for independent researchers environment are in  Barestshire university-environment is an example of Environments in environments \\
\hline
10 &  Identifiers &  A unique identifier for data controller, data processors, a piece of data content, environment, etc & How to uniquely identify process, data, users, controller in GOND and NRDS's environment   \\
\hline
11 & Time Duration and Age & How long the data is collected, processed, and controlled by the various environments during the life cycle. Age of data when it is ready for use    & How long the GOND takes time to pass on data to the NRDS. Might be the one week old data is not more useful for the independent researchers.   \\
\hline


\end{tabularx}
\end{longtable}




\begin{comment}
% this sections is commented 
A simple flow of data in the environments can be complex due to its attached data attributes, context and determining  responsibilities. In order to understand the simple use case of data sharing between environments of data usage that have been subject to disclosure control. Imagine that a local authority wants to analyse how their Parks facilities are being used by the various members of community. Additionally,the local authority's various departments are interested to use park's data for the improvement of their services and effective decisions. For example improving of children and adults facilities,  planting and environment management, finance and funds allocation, etc. For this purpose local authority  have given a task to one of his Park's Management: Mushroom World Park for collecting the personal data of its visiting customers. Call this Environment 1. Environment 1 is the part of Global Environment of Local Authority. In order to get opportunistic  benefit from the data, Mushroom World Park will also use this data for the promotional activities. 

Additionally, to fund the cost of data collection local authority and Mushroom World Park's management have singed  a data sharing  agreement with the external funder call as Mental Health and Wellbeing (MHW) organisation. As part of the agreement that the disclosure-controlled version of dataset will be shared with the MHW. MHW will disseminate the version of collected data to its various research institute to research mental health conditions of people who visiting parks and vs those who never visited. Based on the use case the data will flows from Mushroom World Park to local authority and then to the MHW and then to MHW research institute. 
The data flows in the  Mushroom World Park, various departments of local authority, and MHW defines the parameters of data situation. These parameters information will be used in the ADF to analyse the risk of data sharing and anonymisation decisions through automation processes.

\end{comment}


\begin{comment}
% this sections is commented 
For example, the data environment representation (i.e provenance graph) should be able to answer that: Who are the data subjects, data controllers, and data processors. How Long the data is controlled and processed by the controller and processor in the specific life cycle of data. How it is expected that the data to be used by receiving environment. The provenance graph should also be able to answer that What kind of data the data controller has about the data subjects, e.g. statistics, text and etc. At what level  of information the data provide about the data subjects e.g. microdata, aggregated and etc.  Does the provenance contains  the information of properties of the dataset are, e.g. age, quality, etc.  Further, the representation of data environment should contain information    Where the data is controlled, processed; When the data is deleted permanently by data controller or processor  and to what extent the data subjects are aware of data situation (i.e. controlling, processing, deleting involved in the data lifetime). To understand these requirements lets take a more complex use 
\end{comment}



\begin{table}
\caption{Data Environment Requirements to represent data situation of GOND-NRDS in PROV}\label{tab1}
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{S\#} &  \textbf{Representation Requirement}  &  \textbf{Description}  &  \textbf{Example in GOND-NRDS use case} \\
\hline
01 &  Piece of data  &  A kind of collected, processed, and shared data  &  GOND generate a set of data for NRDS and open environment \\
\hline

02 &  Processes  &  A kind of activity that changes the state of data  or any mechanism that is used for auditing purpose &  A data service at GOND that pass on data by checking some agreement protocols \\
\hline

03 &  Requirement  &  Description  &  Example in GOND-NRDS use case \\
\hline

\end{tabular}
\end{table}


\begin{tabularx}{0.8\textwidth} { 
  | >{\raggedright\arraybackslash}X 
  | >{\centering\arraybackslash}X 
  | >{\raggedleft\arraybackslash}X | }
 \hline
 item 11 & item 12 & item 13 \\
 \hline
 item 21  & item 22  & item 23  \\
\hline
\end{tabularx}





%\begin{longtable}{|p{2.8cm}|p{6cm}|p{8cm}|}
\begin{longtable}{|p{0.22\linewidth}|p{0.48\linewidth}|p{0.6\linewidth}|}
\caption{Data environment representation requirements for GOND-NRDS use case.\label{tab1}}\\

\hline
\rowcolor{Gray}
  \textbf{Representation requirements}  &  \textbf{Description}  &  \textbf{Example in use case} \\
\hline
\endfirsthead

\hline
\rowcolor{Gray}
\textbf{Representation requirements}  &  \textbf{Description}  &  \textbf{Example in use case} \\
\hline
\endhead

 Data Environment Construct &
 Data environment construct defines the contextual boundaries for data controller, data processor,  data users,  data sharing, data situation, etc. 
 %Data environment construct also defines the locus of control and locus of responsibility.
 & GOND and NRDS are two closed data environments with different data and events . Where  output data from the independent researchers in the publications is an open environment that have a different purpose. \\
 \hline
  Data Environments in Data Environments &
  Sometimes an environment may contain other environments along with users, data, and processes. And data flows in the same organisation's sub units for processing, auditing, etc. & NRDS data environment and research lab for independent researchers data environment are in  Barestshire university data environment is an example of environments in environments. \\
\hline
 Attaching Attributes with the Data Environments& 
  This describe the purpose of data collection and type of data environment or any constraints over the data environment  &  GONDs collect data from its partners for effective decision making and sharing of data with public because of legal obligations and its type of government and restricted data environment. Whereas the data shared through publications in the open environment is not a restricted environment. \\   
  \hline
   Relationship among the constructs &
   This describes the possible  relationship from data environment to another data environment or internal elements such as relationship among the piece of data, process, user    &  By using the knowledge from the relationship the information about data subjects can be identified. On the other hand the relations among the data controller, and data users can reduce the risk to the data in the intended data environment. \\
   \hline
   Annotation to the relational constructs  &
   It is the non-functional requirements. The attachment of additional annotation represent the semantic meaning of relationship among the construct &  ** \\
 \hline
 Data controller, data processor, data users and data subjects  &
 To represent data controller and processors,  with their types (i.e. authority, organisation, or individual), tasks and responsibilities within given time and in related data environment. This also represent the information of data subjects and data users (i.e. id, name, age, related consent, contract). &  As GOND  and NRDS is a type of organisation data controller and processor. GOND is data controller with direct responsibility of his environment and indirect responsibility for NRDS environment. GOND is also a data processor, it generate datasets for NRDS and for an open environment.\\
    \hline
  Data and events & 
  A kind of collected, processed, and shared data along with its variables and related events  &  GOND generate a set of datasets for NRDS and for open environment through data extracting, processing and sharing events.  \\
  \hline
  Access and control (Direct and Indirect)  &
  How to show the access and control mechanism over the data and services &  GOND has service that can be accessed by the NRDS  based on some contract signed by them. GOND has also indirect control over the data release from the NRDS environment.  \\
\hline
\end{longtable}